---
title: "Introduction to StatComp22077"
author: "Wei Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp22077}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22077__ is a simple R package as the final homework of the 'Statistical Computing' course. The two extra functions are written in this
package.

The former function can calculate a hessian matrix of the likeihood function.

The concrete code is as follows:

```{r,eval=FALSE}
hessian_i = function(
  data_i, #i^th observation: (Y_i, X_i, Z_i)
  symbolic_hessian, #matrix with elements that are the symbolic expression for the derivatives
  param_vals, #estimates of first stage and second stage parameter estimates (theta and beta)
  dimension #the dimension of the hessian matrix
  ){
  
  env = as.list(c(data_i, param_vals))

  # Iterate through every element in symbolic_hessian and evaluate it
  # at the i^th observation using the given parameter estimates
  hessian = matrix(
    sapply(symbolic_hessian, eval, env = env, enclos = NULL), 
    dimension)
  
  return(hessian)
  
}
```

The latter function is a quick sort algorithm which is written with c++ language.Quicksort is a faster sort method. The basic idea is to sort the data to be sorted into two independent parts by a set of sorting, all the data in one part is smaller than all the data in the other part, and then in this way the two parts of the data are quickly sorted, the whole sorting process can be recursive, so that all the data into an ordered sequence.

The concrete code is as follows:
```{r,eval=FALSE}
int part(int* r, int low, int hight)  
{
  int i = low, j = hight, pivot = r[low]; 
  while (i < j)
  {
    while (i<j && r[j]>pivot) 
    {
      j--;
    }
    if (i < j)
    {
      swap(r[i++], r[j]);  
    }
    while (i < j && r[i] <= pivot) 
    {
      i++;
    }
    if (i < j)
    {
      swap(r[i], r[j--]); 
    }
  }
  return i;  
}
void Quicksort(int* r, int low, int hight)
{
  int mid;
  if (low < hight)
  {
    mid = part(r, low, hight);  
    Quicksort(r, low, mid - 1); 
    Quicksort(r, mid+1, hight); 
  }
}
int main()
{
  int a[10001];
  int  N;
  cout << "Please enter the number of data to sort: " << endl;
  cin >> N;
  cout << "Please enter the data to sort: " << endl;
  for (int i = 0; i < N; i++)
  {
    cin >> a[i];
  }
  cout << endl;
  Quicksort(a, 0, N - 1);
  cout << "The sorted sequence is: " << endl;
  for (int i = 0; i < N; i++)
  {
    cout << a[i] << " ";
  }
  cout << endl;
  return 0;
}
```
